FireSim2019_ManuscriptFigures

### 2023-05-26 README.rmd
Update README.rmd

Scripts for analyzing data associated with "Experimentally-determined traits shape bacterial community composition one and five years following wildfire"

>>>>

Scripts for analyzing data associated with "Experimentally determined traits shape bacterial community composition one and five years following wildfire"
